Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
DSN changes

The highly connected, highly similar differential paths are highlighted in
Figure \ref{Fig:Graph-Clique}: when the neighbors of H. Dobbertin's and
P. Kasselman's collision classes from Figure \ref{Fig:Graph-Intro} are viewed
independently, the large cliques become apparent. Depending on the search
strategies utilized, cliques may be expanded before new neighbors, or a
significant portion of a vertices neighbors might belong to existing cliques,
resulting in slow progress towards any external goal.

Refer to Table \ref{table:distance} for the distances between existing
collisions in MD4.

@@

We find justification for the distance heuristic $\Delta$ in the existing
literature due to collisions by  X. Wang \cite{cryptoeprint:2004:199} and
M. Schl{\"a}ffer \cite{Schlaffer2006}. Their respective families are:
$
\begin{aligned}
F(C_{Wang}) = (& 1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 12, \\
        & \textbf{13}, 15, 16, 19, 20, 35, 36) \\
\end{aligned} \\
\begin{aligned}
F(C_{Schlaffer}) = (& 1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 12, \\
         & 15, 16, 19, 20, 35, 36)
\end{aligned}
$

>>>>

The highly connected, highly similar differential paths are highlighted in
Figure \ref{Fig:Graph-Clique}: when the neighbors of H. Dobbertin's and
P. Kasselman's collision classes from Figure \ref{Fig:Graph-Intro} are viewed
independently, the large cliques become apparent. Depending on the search
strategies utilized, cliques may be expanded before new neighbors, or a
significant portion of a vertices neighbors might belong to existing cliques,
resulting in slow progress towards any external goal, such as finding
a second-preimage attack when distance must be greater than some bound.

We present results in Table \ref{table:distance} which illustrate the
distances found between published collision classes in MD4.

@@

We justify the distance heuristic $\Delta$ in the existing
literature due to collisions by  X. Wang \cite{cryptoeprint:2004:199} and
M. Schl{\"a}ffer \cite{Schlaffer2006}. Their respective families are:
$
\begin{aligned}
F(C_{Wang}) = (& 1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 12, \\
        & \textbf{13}, 15, 16, 19, 20, 35, 36) \\
\end{aligned} \\
\begin{aligned}
F(C_{Schlaffer}) = (& 1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 12, \\
         & 15, 16, 19, 20, 35, 36)
\end{aligned}
$

For this example $\Delta(F(C_{Wang}), F(C_{Schlaffer})) = 1$.
